Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-01-26 paper.tex
update

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major governance challenges faced by researchers (semantic matching and QoS optimisation). Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning. QoS optimisation aims to meet the non-functional requirement of service users. E.g., minimum cost, maximal reliability. Many scholars have looked into nonfunctional optimisation problems in QoS-aware web service composition applying AI planning and Evolutionary Computation techniques. To meet users' requirement, one often needs to consider both semantic matching and QoS optimisation simultaneously. Existing works on web service composition often concerns either semantic service composition or QoS-aware service composition. However, there are few works concerns both quality of semantic matchmaking and quality of services at the same time and points out the benefits clearly. Therefore, In this paper, we consider two quality dimensions in a proposed more applicable comprehensive quality model for semantic web service composition and present an automated semantic web service composition approach that can generate service composition solutions that meet both functional and non-functional requirement.  The results show our method can find better semantic matchmaking quality with a very slight trade off in QoS. Also, we comparing our PSO-based approach with one GP-based approach, our method performs better in finding optimised solution with a trade off in execution time.

@@

Two most notable challenges for web service composition are $(1)$ ensuring interoperability of services and $(2)$ achieving QoS optimisation \cite{fensel2011semantic}. \textit{Interoperability} of web services presents challenge $(1)$ in syntactic and semantics dimensions \cite{fensel2011semantic}. The syntactic dimension is covered by the XML-based technologies (such as $WSDL$, $SOAP$). The semantics aspect, on the other hand, demands further research. Through ontology-based semantics \cite{o2005review}, web services can understand and better collaborate with each other. There are many ontologies languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}, which make ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments. The second challenge $(2)$ is related to finding \textit{optimised solutions} to Quality of Service ($QoS$). This problem gives birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements (SLA) \cite {sahai2002automated} involving a collection of SLA rules and policies for supporting QoS-based composition.

Existing works on service composition focus mainly on addressing the one of challenges above. A lot of works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as \textit{semi-automated Web service composition} approach. Meanwhile, many research works consider the possibility of generating a composite plan automatically in discovering and selecting suitable web services, which are considered to be NP-hard \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, with the hope of eliminating conflicts by the semantic level of web services. In the past few years, substantial works have been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}. However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously. To a given service request, the quality of service composition solution depends on both QoS and quality of semantic matchmaking. Therefore, a comprehensive quality model is needed to measure the quality of service composition solution.

The overall goal of this paper is to \textit{develop an comprehensive quality-aware automated semantic web service composition that satisfactorily optimises both functional and non-functional requirements}. Particularly, this paper extends existing works on semantic service composition and QoS-aware service composition by considering both QoS optimisation and semantic matching optimisation in our comprehensive quality model. Particle Swarm Optimisation (PSO) has show its promise in searching near-optimised service composition solution \cite{da2016particle}, we will propose a PSO-based service composition approach using our comprehensive quality model, which is considered to be more applicable way to measure semantic matchmaking in automated semantic web service composition. We will achieve three objectives in this work as follows:

\begin{enumerate}
 \item To propose a comprehensive quality model that address QoS and semantic matchmaking quality in considering different matching types with corresponding semantic similarity. This approach is consider to be a more applicable and effective way of finding an optimised solution in semantic web service composition.

 \item To propose a PSO-based service composition algorithm that utilises the proposed quality model. To do that we will first propose a representation of semantic service composition, which can model the quality of semantic matchmaking and QoS with the representation. A particle is then used to represent a queue of services that can be used to generate a near-optimised semantic service composition solution.

@@

\section{Related Work} \label{relatedWork}
\textbf{Semantic web service composition}. Substantial work \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} on web service composition focused primarily on non-functional requirements consistently neglecting functional requirements. However few researchers addressed both functional and nonfunctional requirements at the same time in web service composition. To the best of our knowledge, \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} reported some recent attempts on service composition that considers both nonfunctional (QoS) and functional (semantic) aspects. Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} to search for services that ensure semantic matching utilising an ontology of the corresponding domain.

The combination of enhancing planning graph (EPG) and clonal selection algorithm is introduced in the work \cite{pop2009immune}  to solve web service optimisation problem as an immune-inspired web service composition approach. During the clonal selection process, the antigen is represented as a fitness function, and the antibody is represented as a binary alphabet to encode EPG. In this work,  semantic matchmaking is considered by measuring the quality of the similarity measure using information retrieval technique.

In \cite{shet2012new}, three approaches have been studied regarding the similarity measures using taxonomies: The first one is based on nodes, in which similarity is determined by the information content of the nodes; the second is entirely based on edge, where concept distance in a hierarchy structure is evaluated, and third one is the hybrid approach features a combination of these two. A similarity measure based on edge counting in taxonomy is introduced in \cite{shet2012new}. Neighbourhood concepts are considered in their model when $\lambda$ = 1 (default value as 0).

@@

The work \cite{fanjiang2014semantic} concerns both functional and non-functional requirements in design time of semantic-based automatic service composition, where a GA-based approach with four unusual independent fitness functions are designed to solve the problems with these concerns. A sequence of fitness functions are used in the binary selection of chromosomes, rather than a single objective consisting of both functional and non-functional quality. Apart from that, match types are ignored in their quality evaluation of semantic matching.

\textbf{QoS-aware EC approaches}. Evolutionary Computation techniques are widely used to solve optimisation problems, where the search space is big, so that near-optimised solutions can be found in reasonable time. Genetic Programming (GP) \cite{da2015graphevol} is a typical EC technique applied to automated web service composition. GP-based approaches utilise tree representations, on which service and constructs are represented as terminal nodes and functional nodes respectively. The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure.

Gupta et al. \cite{gupta2015optimization} proposed an improved Genetic Algorithm for QoS-ware web service composition, where some population associated with lower fitness are discarded with bringing in new offerings in each generation.

In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions. Also, this paper increase the mutation rate while encountering low diversity in the population and adopt a higher crossover probability while trapped in local optimisation.

A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of Directed Acyclic Graph(DAG) employing Graph-based evolutionary operators like crossover and mutation.

A hyper approach employs both a greedy search algorithm and genetic programming is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness. In particularly, the greedy search is used to the directed acrylic graph as composite solutions, which is further transferred to tree structure using unfolding techniques as the first generation in GP. In each individual,  terminal nodes are considered as task inputs,  root node as outputs, and inner nodes as atomic web services. During the reproduction process,  a randomly selected node in one individual is replaced with a new subtree generated by a greedy search to perform mutation while same atomic inner nodes in two random chosen individuals are swapped to perform crossover.

To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}. A general graph is used as representation as composite solution in their PSO algorithm considering QoS optimisation.

@@

However, composite solutions from \cite{qi2010combining,da2016particle,ma2015hybrid,da2015graphevol,yu2013adaptive} does not consider distinguished matchmaking quality in their fitness function, which might lead to over-general outputs to be produced by selected services, The finding is evidently supported by comparing two different evaluation model in Sect. \ref{comparisonTest}. In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users. In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and parameter similarity to determine the overall quality of web service composition. Weighed graphs are also utilised in PSP to facilitate a new representation of web service composition adopted from \cite{da2016particle}.
\section{Problem Description}\label{problemDes}

@@

\begin{figure*}[h]
\centering
\fbox{\includegraphics[scale=.4]{overview.pdf}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure*}

In this section, we propose a comprehensive quality model for automated semantic service composition, and optimise both the quality of semantic matchmaking and QoS. PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}. Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing that often required by GP \cite{da2016particle}. Fig. \ref{overview} shows the overview of our approach with five steps. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional. Step 2: This composition goal are used to discover all relevant web services, which lead to a shrunken service repository that is subsequently used by PSO as a searching space. Step 3: A weighted graph representation is randomly built up from the an initial service queue that mapped to the particle's location, interleaving with semantic matchmaking process utilising ontology-based index cache. In the weighted graph, graph edges are assigned with semantic matchmaking quality as weights. Step 4: The fitness value of the weighted graph is evaluated to update the position of particle under PSO algorithm in Sect. \ref{pso_algorithm}, where the position is mapped to the index of service queue. later on, the updated service queue is used to decode a new weighted graph as the composition solution. Step 4. Lastly, the best position found in the searching space is selected and decode into the final optimised solution. This PSO-based approach is different from \cite{da2016particle}, as we use weighted graphs as solution presentation.

@@

\subsection{Ontology-based Index Cached Optimisation}\label{indexCache}
In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively. To effectively construct weighted graphs, we pre-calculate semantic matchmaking quality and mark the input-parameter concepts with a set of services. The key idea of the index is to create a mapping from the output-related concepts to matched input-related services while considering different levels of match types. Furthermore, this index size could also be reduced by only considering parameter-related concepts in the shrunken service repository, which contains  those task-relevant web services. This optimised cache also contributes to less and constant time for weighted graph building for the whole evolutionary process.

@@

\textbf{Semantic matchmaking model}. Due to the discretisational characteristics of different match types and values assigned to matching types that driven by the cost of data integration and manipulation \cite{lecue2009optimizing}, partial ordering match types are considered to be one factor for the semantic matchmaking quality. For example, Exact matching type demands less time for computation compared to that of Plugin match. Another factor in our proposed model is concept similarity, which could be evaluated based on the edge counting method defined in \cite{shet2012new}. This formula (\ref{equation1}) is used to estimate the similarity between parameter-related output concept and parameter-related input concept for selecting web services. Therefore, given the quality match type and the similarity of two parameters-related concepts, the semantic matchmaking quality of matched parameters is defined by Formula (\ref{equation2}), where the value of $q(p_ {mt})$ follows the same settings in \cite{lecue2009optimizing}. Particularly, 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).

@@

\subsection{Fitness Calculation}
In real life, given a unique and optimised solution is always easier for customers choose from when many quality criteria involved in the composite solution, rather than provided a set of solutions. Therefore, it is very practical to define a single fitness as a weighted sum of all the quality related components in Formula (\ref{equation6}), where weights setting is very flexible, it could be adjusted according to users' preferences. The fitness value of 1 means the best comprehensive quality and 0 means the worst. For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the fitness value falls within the range from 0 to 1. Therefore, the service composition problem in this paper is treated as a fitness maximisation problem.
\vspace{-0.2cm}
\begin{equation}
\label{equation6}
Fitness = w_1 \hat{MT} + w_2 \hat{S} + w_3 \hat{A} + w_4 \hat{R} + w_5(1 - \hat{T}) + w_6(1 - \hat{C})
\end{equation}
\noindent where $\sum_{i=1}^{6} w_i = 1$
\\
\vspace{-0.2cm}
\begin{equation}
\label{equation7}
\hat{Q_k} = 
\begin{cases}
	\frac{Q_k - Q_{k, min}}{Q_{k, max} - Q_{k, min}} & \text{ if }Q_{k, max} - Q_{k, min} \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\noindent where $k$ $=$ $1$, $2$, $3$, and $4$, where $Q_1$ as $MT$, $Q_2$ as $S$, $Q_3$ as $A$, and $Q_4$ as $R$.
\begin{equation}
\label{equation8}
\hat{Q_j} = 
\begin{cases}
	\frac{Q_{j,max} - Q_j}{Q_{j, max} - Q_{j, min}} & \text{ if }Q_{j, max} - Q_{j, min} \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\noindent where $j$ $=$ $1$, and $2$, where $Q_1$ as $T$ and $Q_2$ as $C$.

@@

\begin{algorithm}[!htb]
 \setlength\hsize{0.9\linewidth}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \let\oldnl\nl% Store \nl in \oldnl
\newcommand{\nonl}{\renewcommand{\nl}{\let\nl\oldnl}}
 \LinesNumbered
 	\textbf{1.} Map each relevant service to an index in the particle's position vector.\\
	\textbf{2.} Randomly initialise each particle in the swarm.\\
	\nonl \While {max. iterations not met}{
		\ForAll{particles in the swarm}{
		    \textbf{3.} Create queue of services using the particle's position vector.\\
			{\textbf{4.} $WG \leftarrow$ generatedWeigthedGraph().}\\
			{\textbf{5.} Calculate the $WG$ fitness value.}\\
			\eIf{fitness value better than pBest}{
				\textbf{6a.} Assign current fitness as new pBest.\\
			}{
				\textbf{6b.} Keep previous pBest.\\
			}		
		}
		\textbf{7.} Assign best particle's \emph{pBest} value to \emph{gBest}, if better than gBest.\\
		\textbf{8.} Calculate the velocity of each particle according to the equation:\\
		\Indp $v_{id} = v_{id} + c_1 * rand() * (p_{id} - x_{id}) + c_2 * rand() * (p_{gd} - x_{id})$\\
		\Indm \textbf{9.} Update the position of each particle according to the equation:\\
		\Indp $x_{id} = x_{id} + v_{id}$\\
	}

 \caption{Steps of the PSO-based Web service composition technique.}
\label{novelSteps}
\end{algorithm}

\begin{algorithm}
 \setlength\hsize{0.9\linewidth}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{generateWeightedGraph}{generateWeightedGraph}
 \SetKwProg{Procedure}{Procedure}{}{}
 \LinesNumbered
 \SetNlSty{}{}{:}
  \Procedure{\generateWeightedGraph{}}{
 \Input{Task inputs $I$, task outputs $O$, relevant Web services $queue$, IndexCache $IndexCache$}
 \Output{Weighted Graph $WG$}
 $WG \leftarrow  null$\;
 $WG \leftarrow$ new $endNode$(), new $startNode$()\;
 $OutputSet \leftarrow$ \{$I$\}\;
  \While {all $O$ $\notin$ $OutputSet$  and $queue !=null$}{
     \ForEach{$ws$ in $queue$}{
      \uIf{$ws.inputs$ $\in$ $OutputSet$ }{    
    		 \ForEach{$I$ in $ws.inputs$}{
    		$parameter.matchType \leftarrow$ query $IndexCache$\;
     		$parameter.conceptSiminarity \leftarrow$ query $IndexCache$\;
              }
        $WG.edge \leftarrow$ new $Edge$()\;
        $edge.weights \leftarrow$ aggregation($parameters$)\;
        $WG \leftarrow$ new $wsNode$()\;
         $OutputSet$ add \{$ws.outputs$\}\;    
       $queue$.remove $ws$\;
       }	
     }
  }
 remove $dangling nodes$\; 
 remove $dangling edges$\;
 \KwRet $WG$\;
 }
 \vspace{2mm}
 \caption{Create a composition weighted graph from a queue.}
\label{graph_building}
\end{algorithm}

The overall algorithm investigated here is made up of a PSO-based web service composition algorithm \ref{novelSteps} and a decoding algorithm \ref{graph_building}, to generate a composition weighted graph. In algorithm \ref{novelSteps}, the idea is to translate the particle location produced by PSO into a service queue as an indirect representation of weighted graph, such that finding the best fitness of the weighted graph is to discover the optimised location of the particle in the search space. In PSO, the dimension of each particle equals to the number of relevant web services. The index of each services is mapped to a separate location component in a particle. Services in a queue follow the ascending order, from which we decode a weighted graph using Algorithm \ref{graph_building}. We select and connect  service node to the start node from the service queue if the inputs of web service can satisfy the output of start node. The edge associated with two connected nodes is also created, the weight of which is also calculated as a quality aggregated value from concept-related parameters. Meanwhile, an Output Set is initialised and kept being updated using outputs from the newly added service node in the weighted graph, later on, more services vertices are connected with edges if services' inputs could be satisfied by any output in the Output Set. Finally, the end vertex is connected to the graph if the updated Output Set contains all end inputs. In addition, dangling service vertex and edges will be removed. 
\section{Experiment Design}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design. The objectives of the evaluation are to $(1)$ measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach; $(2)$ explore the impacts of the semantic matchmaking that contributes to overall composition quality; and $(3)$ compare solutions generated by QoS-ware approach with our method.

@@

We also study the average fitness value with the optimum through the evolutionary process for both PSO-based and GP-based approach over 30 independent runs. Fig. \ref{psovsgp} is an example of convergence rate from Task 3, where the behaviour of PSO-based approach presents a very clear evidence of fast convergence and reaches a better-optimised solution, while the performance of GP is barely satisfactory, as this method improves its fitness value gradually.

>>>>

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major governance challenges faced by researchers (semantic matchmaking and QoS optimisation). Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning. QoS optimisation aims to optimise the non-functional requirement of service users. E.g., minimum cost, maximal reliability. Many scholars have looked into nonfunctional optimisation problems in QoS-aware web service composition applying AI planning and Evolutionary Computation techniques. To meet users' requirement, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition often concerns either semantic service composition or QoS-aware service composition. However, there are few works concerns both quality of semantic matchmaking and quality of services at the same time and points out the benefits clearly. Therefore, In this paper, we consider two quality dimensions in a proposed more applicable comprehensive quality model for semantic web service composition and present an automated semantic web service composition approach that can generate service composition solutions that meet both functional and non-functional requirement.  The results show our method can find better semantic matchmaking quality with a very slight trade off in QoS. Also, our method performs better in finding optimised solution with a trade off in execution time comparing an existing GP-based method.

@@

Two most notable challenges for web service composition are $(1)$ ensuring interoperability of services and $(2)$ achieving QoS optimisation \cite{fensel2011semantic}. \textit{Interoperability} of web services presents challenge $(1)$ in syntactic and semantics dimensions. The syntactic dimension is covered by the XML-based technologies (such as $WSDL$, $SOAP$). The semantics aspect, on the other hand, demands further research. Through ontology-based semantics \cite{o2005review}, web services can understand and better collaborate with each other. There are many ontologies languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}, which make ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments. The second challenge $(2)$ is related to finding \textit{optimised solutions} to Quality of Service ($QoS$). This problem gives birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements (SLA) \cite {sahai2002automated} involving a collection of SLA rules and policies for supporting QoS-based composition.

Existing works on service composition focus mainly on addressing the one of challenges above. A lot of works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as \textit{semi-automated Web service composition} approach. Meanwhile, many research works consider the possibility of generating a composite plan automatically in discovering and selecting suitable web services, which are considered to be NP-hard \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, with the hope of eliminating conflicts by the semantic level of web services. In the past few years, substantial works have been done on semantic web service composition \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune}. However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously. To a given service request, the quality of service composition solution depends on both QoS and quality of semantic matchmaking. Therefore, a comprehensive quality model is needed to be addressed, and more methods are needed to be applied specifically on the problem that optimises semantic matchmaking quality and QoS simultaneously.

The overall goal of this paper is to \textit{develop an comprehensive quality-aware automated semantic web service composition that satisfactorily optimises both functional and non-functional requirements}. Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matching optimisation in our proposed comprehensive quality model. Particle Swarm Optimisation (PSO) has show its promise in searching near-optimised service composition solution \cite{da2016particle}, we will propose a PSO-based service composition approach using our comprehensive quality model, which is also considered to be more applicable way to measure semantic matchmaking in automated semantic web service composition. We will achieve three objectives in this work as follows:

\begin{enumerate}
 \item To propose a comprehensive quality model that address QoS and semantic matchmaking quality in considering different matching types with corresponding concept similarity. This method is consider to be a more applicable and effective way of finding an optimised solution in semantic web service composition.

 \item To propose a PSO-based service composition algorithm that utilises the proposed quality model. To do that we will first propose a representation of semantic service composition, which can model the quality of semantic matchmaking and QoS together. A particle is then used to represent a queue of services that can be used to decoded into a near-optimised semantic service composition solution.

@@

\section{Related Work} \label{relatedWork}
\textbf{Semantic web service composition}. Substantial work \cite{da2016particle,bansal2016generalized,mier2015integrated,da2015graphevol,yu2013adaptive} on web service composition focused primarily on non-functional requirements consistently neglecting functional requirements. However few researchers addressed both functional and nonfunctional requirements at the same time in web service composition. To the best of our knowledge, \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} reported some recent attempts on service composition that considers both nonfunctional (QoS) and functional (semantic) aspects. Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} to search for services that ensure semantic matching utilising an ontology of the corresponding domain.

The combination of enhancing planning graph (EPG) and clonal selection algorithm is introduced in the work \cite{pop2009immune} as an immune-inspired web service composition approach. During the clonal selection process, the antigen is represented as a fitness function, and the antibody is represented as a binary alphabet to encode EPG. In this work,  semantic matchmaking is considered by measuring the quality of the similarity measure using information retrieval technique.

@@

The work \cite{fanjiang2014semantic} concerns both functional and non-functional requirements in design time of semantic-based automatic service composition, where a GA-based approach with four unusual independent fitness functions are designed to solve the problems with these concerns. A sequence of fitness functions are used in the binary selection of chromosomes, rather than a single objective consisting of both functional and non-functional quality. Apart from that, semantic matching types are ignored in their quality evaluation of semantic matching.

\textbf{QoS-aware web service composition}. Evolutionary Computation techniques are widely used to solve optimisation problems, where the search space is big, so that near-optimised solutions can be found in reasonable time.

Gupta et al. \cite{gupta2015optimization} proposed an improved Genetic Algorithm for QoS-ware web service composition, where some population associated with lower fitness are discarded with bringing in new offerings in each generation. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions. Also, this paper increase the mutation rate while encountering low diversity in the population and adopt a higher crossover probability while trapped in local optimisation. A hyper approach employs both a greedy search algorithm and genetic programming is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness. In particularly, the greedy search is used to generate directed acrylic graph as composite solutions, which is further transferred to tree structure using unfolding techniques for initialisation and mutation during the evolutionary process. A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of Directed Acyclic Graph(DAG) employing Graph-based evolutionary operators like crossover and mutation. To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}. A general graph is used as representation as composite solution in their PSO algorithm considering QoS optimisation.

@@

However, composite solutions from \cite{qi2010combining,da2016particle,ma2015hybrid,da2015graphevol,yu2013adaptive} does not consider distinguished matchmaking quality in their fitness function, which might lead to over-general outputs to be produced by selected services, The finding is evidently supported by comparing two solutions employing different evaluation model in Sect. \ref{comparisonTest}. In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users. In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and parameter-related concept similarity to determine the overall quality of web service composition. Also, Weighed graphs are utilised as representationd of semantic web service composition decoded from optimised service queue using PSO adopted from \cite{da2016particle}.
\section{Problem Description}\label{problemDes}

@@

\begin{figure*}[h]
\centering
\fbox{\includegraphics[scale=.4]{overview.pdf}}
 \caption{Overview of POS-based automated semantic web service composition approach.}
 \label{overview}
\end{figure*}

In this section, we propose a comprehensive quality model for automated semantic service composition, and optimise both semantic matchmaking quality and QoS. PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}. Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing that often required by GP \cite{da2016particle}. Fig. \ref{overview} shows the overview of our approach with five steps. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional. Step 2: This composition goal are used to discover all relevant web services, which lead to a shrunken service repository that is subsequently used by PSO as a searching space. Step 3: A weighted graph representation is randomly built up from the an initial service queue that mapped to the particle's location, interleaving with semantic matchmaking process utilising ontology-based index cache. In the weighted graph, graph edges are assigned with semantic matchmaking quality as weights. Step 4: The fitness value of the weighted graph is evaluated to update the position of particle under PSO algorithm in Sect. \ref{pso_algorithm}, where the position is mapped to the index of service queue. later on, the updated service queue is used to decode a new weighted graph as the composition solution. Step 4. Lastly, the best position found in the searching space is selected and decode into the final optimised solution. This PSO-based approach is similar to \cite{da2016particle}, but we employ weighted graphs as a different solution presentation.

@@

\subsection{Ontology-based Index Cached Optimisation}\label{indexCache}
In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively. To effectively construct weighted graphs, we pre-calculate semantic matchmaking quality. The key idea of the index is to create a mapping from the output-related concepts to potentially matched input-related concepts while considering different levels of match types. Meanwhile, this index size could also be reduced by only considering the concepts related in the shrunken service repository, which means the index cache is filtered by those task-relevant web services. This optimised cache also contributes to less and constant time for weighted graphs building through the whole evolutionary process.

@@

\textbf{Semantic matchmaking model}. Due to the discretisational characteristics of different match types and values assigned to matching types that driven by the cost of data integration and manipulation \cite{lecue2009optimizing}, partial ordering match types are considered to be one factor for the semantic matchmaking quality. For example, Exact matching type demands less time for computation compared to that of Plugin match. Another factor in our proposed model is concept similarity, which could be evaluated based on the edge counting method defined in \cite{shet2012new}. This formula (\ref{equation1}) is used to estimate the similarity between concept-related parameters for selecting web services. Therefore, given the quality match type and the concept similarity of two parameters-related concepts, the semantic matchmaking quality of matched parameters is defined by Formula (\ref{equation2}), where the value of $q(p_ {mt})$ follows the same settings in \cite{lecue2009optimizing}. Particularly, 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).

@@

\subsection{Fitness Calculation}
In real life, given a unique and optimised solution is always easier for customers to pick up directly when many quality criteria involved into decision making, rather than provided a set of solutions. Therefore, it is very practical to define a single fitness as a weighted sum of all the quality related components in Formula (\ref{equation6}), where weights setting is very flexible, it could be adjusted according to users' preferences. The fitness value of 1 means the best comprehensive quality and 0 means the worst. For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the fitness value falls within the range from 0 to 1. Therefore, the service composition problem in this paper is treated as a fitness maximisation problem.
\vspace{-0.2cm}
\begin{equation}
\label{equation6}
Fitness = w_1 \hat{MT} + w_2 \hat{S} + w_3 \hat{A} + w_4 \hat{R} + w_5(1 - \hat{T}) + w_6(1 - \hat{C})
\end{equation}
\noindent where $\sum_{i=1}^{6} w_i = 1$
\\
\vspace{-0.2cm}
\begin{equation}
\label{equation7}
\hat{Q_k} = 
\begin{cases}
	\frac{Q_k - Q_{k, min}}{Q_{k, max} - Q_{k, min}} & \text{ if }Q_{k, max} - Q_{k, min} \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\noindent where $k$ $=$ $1$, $2$, $3$, and $4$, where $Q_1$ as $MT$, $Q_2$ as $S$, $Q_3$ as $A$, and $Q_4$ as $R$.
\begin{equation}
\label{equation8}
\hat{Q_j} = 
\begin{cases}
	\frac{Q_{j,max} - Q_j}{Q_{j, max} - Q_{j, min}} & \text{ if }Q_{j, max} - Q_{j, min} \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\noindent where $j$ $=$ $1$, and $2$, where $Q_1$ as $T$ and $Q_2$ as $C$.

@@

\begin{algorithm}
 \setlength\hsize{0.9\linewidth}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{generateWeightedGraph}{generateWeightedGraph}
 \SetKwProg{Procedure}{Procedure}{}{}
 \LinesNumbered
 \SetNlSty{}{}{:}
 \Input{relevant Web services $rws$}
 \Output{Optimised service queue $queue$,Optimised Weighted Graph $OPTWG$}
 Map each relevant service to an index in the particle's position vector\;
 Randomly initialise each particle in the swarm\;
  \While {max. iterations not met}{
     \ForEach{particles in the swarm}{
     $queue \leftarrow$ particle's position vector\;
     $WG \leftarrow$ $generateWeightedGraph$()\;
	 Calculate the $WG$ fitness value\;

      \eIf{fitness value better than pBest }{    
        Assign current fitness as new pBest\;
       }{
        Keep previous pBest\;
       }	
     }
    Assign best particle's \emph{pBest} value to \emph{gBest}, if better than gBest\;
 	Calculate the velocity of each particle\;
  	Update the position of each particle\;
  }
 \KwRet $OPTWG$\;
 \caption{Steps of the PSO-based Web service composition technique.}
\label{novelSteps}
\end{algorithm}

\begin{algorithm}
 \setlength\hsize{0.9\linewidth}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{generateWeightedGraph}{generateWeightedGraph}
 \SetKwProg{Procedure}{Procedure}{}{}
 \LinesNumbered
 \SetNlSty{}{}{:}
  \Procedure{\generateWeightedGraph{}}{
 \Input{Task inputs $I$, task outputs $O$, Optimised service queue $queue$, IndexCache $IndexCache$}
 \Output{Weighted Graph $WG$}
 $WG \leftarrow  null$\;
 $WG \leftarrow$ new $endNode$(), new $startNode$()\;
 $OutputSet \leftarrow$ \{$I$\}\;
  \While {all $O$ $\notin$ $OutputSet$  and $queue !=null$}{
     \ForEach{$ws$ in $queue$}{
      \uIf{$ws.inputs$ $\in$ $OutputSet$ }{    
    		 \ForEach{$I$ in $ws.inputs$}{
    		$p_{mt} \leftarrow$ query $IndexCache$\;
     		$p_{s} \leftarrow$ query $IndexCache$\;
              }
        $e_{sm} \leftarrow$ aggregation($p_{mt}$,$p_{s}$)\;
        $WG.edge \leftarrow$  $e_{sm} $\;
        $WG \leftarrow$ new $wsNode$()\;
         $OutputSet$ add \{$ws.outputs$\}\;    
       $queue$.remove $ws$\;
       }	
     }
  }
 remove $dangling nodes$\; 
 remove $dangling edges$\;
 \KwRet $WG$\;
 }
 \caption{Create a composition weighted graph from a queue.}
\label{graph_building}
\end{algorithm}

The overall algorithm investigated here is made up of the PSO-based web service composition algorithm \ref{novelSteps} and the decoding algorithm \ref{graph_building}. In algorithm \ref{novelSteps}, the idea is to translate the particle location produced by PSO into a service queue as an indirect representation, such that finding the best fitness of the weighted graph is to discover the optimised location of the particle in the search space. In PSO, the dimension of each particle equals to the number of relevant web services. The index of each services is mapped to a separate location component in a particle. Services in a queue follow the ascending order, from which we decode a weighted graph using Algorithm \ref{graph_building}. It is a simple forward graph building algorithm, and this method can lead to more services and edges connected to the graph as redundancies that must be removed. Also, semantic quality value are assigned to all the edges, which is calculated from a quality aggregation function from all involved concept-related parameters.

\section{Experiment Design}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design. The objectives of the evaluation are to $(1)$ measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach; $(2)$ explore the impacts of the semantic matchmaking that contributes to overall composition quality; and $(3)$ compare solutions generated by QoS-ware approach with our method; and $(4)$ compare our method with one existing GP-based approach.

@@

At last, We also compare the average fitness value with optimum through the evolutionary process for both two approaches over 30 independent runs. Fig. \ref{psovsgp} is an example of convergence rate from Task 3, where the behaviour of PSO-based approach presents a very clear evidence of fast convergence and reaches a better-optimised solution, while the performance of GP is barely satisfactory, as GP-based method improves its fitness value gradually.
